% LaTeX resume using res.cls
\documentclass[margin]{res} 
\setlength{\textwidth}{5.1in} % set width of text portion
\usepackage{latexsym}
\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Benjamin C. Gordon}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{420 University Ave.}
 \moveleft.5\hoffset\centerline{Los Gatos, CA 95032}
 \moveleft.5\hoffset\centerline{408.489.5690}
 \moveleft.5\hoffset\centerline{bcgordon@ucsc.edu}
 \moveleft.5\hoffset\centerline{\today}

\begin{resume}
\section{OBJECTIVE}  Obtain an internship in which I can expand my software development skills. 
\section{EDUCATION}       
                3rd year student, University of California, Santa Cruz\\ 
                Expected graduation in 2015 \\
                Major: Computer Science \\
 		Current GPA: 3.3
\section{RELEVANT COURSEWORK} 
		{\sl CMPS 20: Game Design Experience} \hfill Winter 2014\\
                \begin{itemize}  \itemsep -2pt %reduce space between items
              		\item Developed a puzzle game in Javascript (titled Antigen) with a team over a period of 8 weeks. The 				game weighs in at around 2200 lines of code.
			\item Learned Javascript and SVN on my own; gained valuable experience developing high-level code with a team. Had to learn to manage and account for team members of varying levels of skill and initiative.
			\item During final presentations, professor urged the entire class to play our game, stating that it was fun and 				interesting. He did not make such statements for any other presentation. 
                \end{itemize}
 
                {\sl CMPS 101: Algorithms} \hfill Fall 2013\\
                \begin{itemize}  \itemsep -2pt %reduce space between items
		        \item Implemented Depth-First Search, Dijkstra’s Shortest Path Algorithm, and Prim’s MST Algorithm on
			directed \& undirected graphs in C99.
			\item Class also covered topics including comparison-based sorting algorithms, heaps, analysis of
			asymptotic growth rates of functions, and logical proofs. 
                \end{itemize} 

                {\sl CMPS 12B: Abstract Data Structures} \hfill Winter 2013\\
                \begin{itemize} \itemsep -2pt
                	\item Implemented numerous data structures in both C and Java. Examples include hash tables, linked
			lists, binary search trees, queues and stacks. Code written in C included memory management.
			\item Gained a functional knowledge of the Gnu Debugger and Valgrind.
			\item Earned 7th highest score out of 147 students on midterm exam. 
                \end{itemize} 
\section{PREVIOUS WORK EXPERIENCE}
                {\sl Summer HR Intern – Affymetrix, Inc. (Santa Clara, CA)} \hfill July – Aug., 2011 \\
			\begin{itemize} \itemsep -2pt
			\item Performed Boolean searches, on-line research, sourcing. Worked with Peoplefluent and Taleo
			ATS systems.
			\item Designed and laid-out company newsletter, using Microsoft Office Publisher.
			\end{itemize}
\section{OTHER SKILLS \& EXPERIENCE}
		Experience developing in Java, Javascript\slash HTML\slash CSS, C, Python, and Assembly\\
		Quick learner with enthusiasm for learning new technologies\\
		Examplary written and verbal communication skills\\
		This resume was typeset in \LaTeXe

\end{resume}
\end{document}




